%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Doomsday Explorer
% Revision 1 (GPT-5.5)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage{arxiv}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage{algpseudocode}

\usetikzlibrary{
arrows.meta,
positioning,
shapes.geometric,
fit,
backgrounds
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{
Doomsday Explorer:
A Decentralized Framework for Iterative Verification of
Classical and Quantum Entropy Claims
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{
Dmytr\'{o} Kondratiuk\\
for peer review
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

Entropy is a foundational assumption of modern cryptography.
Secure key generation, authentication protocols,
digital signatures, blockchain systems,
and numerous distributed protocols ultimately rely on
physical or computational processes that are assumed to be
unpredictable.
Current certification methodologies,
including statistical randomness testing,
entropy estimation,
and quantum validation protocols,
provide empirical evidence that observed sequences are
consistent with expected random behavior under specified assumptions.
However,
no finite collection of statistical tests can establish the
absence of deterministic structure,
implementation-specific vulnerabilities,
or alternative physical explanations.

This paper presents
\emph{Doomsday Explorer},
a decentralized framework for continuously evaluating
competing entropy hypotheses through independently replicated
experimentation.
Rather than introducing another randomness test,
the framework provides an open computational infrastructure
for evaluating both established certification assumptions
and newly proposed models using identical experimental procedures.

Explorer Nodes formulate computational experiments,
while Entropy Miners execute workloads independently.
Selected tasks are replicated across multiple participants,
allowing verification of published results,
detection of inconsistent computations,
and resistance to result withholding.
The resulting body of evidence is publicly reproducible
and evolves continuously as additional experiments are performed.

The framework is intentionally agnostic regarding the correctness
of any individual entropy model.
Instead,
it provides a methodology through which
classical thermal-noise generators,
quantum random number generators,
and future entropy sources
can be evaluated under a common decentralized process.
Confidence is therefore accumulated through
iterative approximation,
independent replication,
and publicly verifiable computation
rather than centralized authority or one-time certification.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Entropy occupies a unique position in modern information security.
Unlike many cryptographic assumptions,
the unpredictability of entropy sources cannot be established solely
through mathematical proof.
Instead,
confidence is typically derived from
physical models,
engineering analysis,
and statistical validation of experimentally observed output.

Classical true random number generators (TRNGs)
derive entropy~\cite{shannon1949} from physical phenomena such as thermal noise,
oscillator jitter,
or electronic avalanche processes.
Quantum random number generators (QRNGs)
derive entropy from measurements~\cite{bell1964} commonly interpreted as
intrinsically probabilistic quantum events.
Both approaches have motivated extensive research,
standardization,
and certification procedures,
culminating in widely adopted testing methodologies such as
the NIST Statistical Test Suite,
entropy estimation procedures,
and complementary validation frameworks.

These methodologies provide valuable evidence that
observed output is statistically consistent with
expected random behavior.
However,
statistical consistency alone cannot prove the absence of
previously unknown deterministic mechanisms,
implementation-specific artifacts,
experimental bias,
or incomplete physical models.
Consequently,
entropy validation remains an empirical scientific process
rather than a mathematically complete proof of unpredictability.

Recent work published through the Doomsday Explorer project
investigates both classical and quantum entropy sources
using large-scale computational analysis,
interactive experimentation,
and publicly reproducible workflows.
Rather than presenting isolated experimental claims,
the project seeks to establish a methodology through which
competing explanations may be evaluated under identical
experimental conditions.

The central contribution of this paper is therefore
methodological rather than adversarial.
Instead of proposing another statistical randomness test,
we present a decentralized framework
for continuous experimental verification of entropy-related hypotheses.
Independent participants execute computational workloads,
replicate selected experiments,
and publish reproducible evidence that may either reinforce
or challenge existing assumptions.
Importantly,
the same infrastructure evaluates
conventional certification methodologies,
newly proposed entropy models,
and the framework's own predictions
using identical computational procedures.

This perspective shifts entropy validation
from one-time certification toward
iterative scientific verification.
Confidence emerges not from the authority of
individual organizations,
vendors,
or research groups,
but from reproducible evidence accumulated through
independent experimentation.
The proposed framework therefore complements existing standards
by enabling continuous public evaluation of
both established assumptions
and unconventional hypotheses.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Motivation}

Modern cryptographic systems increasingly depend upon
entropy sources whose internal operation cannot be
independently reproduced by every relying party.
Certification procedures necessarily evaluate
observable statistical behavior,
physical implementation,
and engineering assumptions.
While these approaches have proven highly valuable,
their conclusions remain conditional upon the correctness
of the underlying models and experimental methodology.

Scientific progress has historically emerged through
continuous replication rather than permanent certification.
As computational resources become globally distributed,
it becomes practical to apply the same principle
to entropy research itself.
Instead of relying exclusively on centralized laboratories,
independent participants may execute identical experiments,
compare results,
and collectively refine confidence in competing hypotheses.

The Doomsday Explorer framework adopts this philosophy.
Its objective is not to replace existing certification,
nor to assume the correctness of any particular entropy model.
Instead,
it provides an open infrastructure
through which empirical evidence may be accumulated,
verified,
and continuously re-evaluated
as new theoretical models,
experimental techniques,
and computational capabilities emerge.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Contributions}

The principal contributions of this work are summarized below.

\begin{enumerate}[leftmargin=1.2cm]

\item
A decentralized computational framework
for reproducible evaluation of entropy-related hypotheses.

\item
A replicated execution model
that mitigates result withholding,
enables independent verification,
and supports public reproducibility.

\item
A unified experimental methodology
applicable to both classical and quantum entropy sources.

\item
An iterative approximation process
through which confidence in competing entropy models
may evolve as additional evidence becomes available.

\item
An open scientific infrastructure
designed to complement,
rather than replace,
existing statistical validation standards, by enabling investigation of unresolved questions concerning the physical and computational origin origin of entropy rather than statistical properties of observed output.

The proposed framework intentionally separates engineering certification from ongoing scientific investigation. Existing statistical validation standards remain valuable for evaluating observable properties of generated sequences, whereas the present methodology focuses on unresolved questions concerning the physical and computational mechanisms capable of producing those observations.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Related Work}

Randomness evaluation has traditionally been approached through
statistical hypothesis testing,
entropy estimation,
physical characterization,
and implementation analysis.
Widely adopted standards,
including the NIST Statistical Test Suite,
Dieharder,
TestU01,
and SP~800-90B entropy estimation~\cite{nist80090b},
provide practical methods for evaluating statistical properties
of generated sequences.
These methodologies have substantially improved
the engineering quality of deployed entropy sources
and remain essential components of modern cryptographic practice.

Quantum random number generators introduce additional
validation techniques derived from quantum mechanical models,
Bell-type experiments,
and device characterization.
While these approaches strengthen confidence in physical implementations,
their conclusions remain dependent upon
experimental assumptions,
measurement fidelity,
and the interpretation of observed phenomena.

Distributed computation has likewise evolved considerably through
volunteer computing,
blockchain consensus,
distributed verification,
and decentralized scientific collaboration.
These systems demonstrate that large-scale computational tasks
can be executed reliably by independent participants,
provided appropriate mechanisms exist
for verification and fault tolerance.

The present work combines these directions.
Rather than proposing a new statistical randomness test
or a replacement cryptographic primitive,
Doomsday Explorer applies decentralized replicated competitive computation
to the scientific evaluation of entropy itself.
The resulting framework treats both established assumptions
and newly proposed hypotheses
as experimentally testable models whose confidence
may be continuously refined through publicly reproducible evidence.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{System Model}

The Doomsday Explorer framework is organized as a decentralized
scientific computation network whose purpose is the reproducible
evaluation of entropy-related hypotheses.
Unlike conventional distributed computation systems,
the objective is not merely computational throughput,
but independent replication,
transparent verification,
and continuous accumulation of empirical evidence.

Three logical components participate in the framework:

\begin{itemize}

\item
\textbf{Explorer Nodes}
formulate experimental workloads,
define computational parameters,
and publish experiment descriptions.

\item
\textbf{Entropy Miners}
independently execute computational tasks,
produce experimental observations,
and return reproducible results.

\item
The
\textbf{Decentralized Verification Network}
coordinates task distribution,
selective replication,
result aggregation,
and publication of experimental evidence.

\end{itemize}

No participant is assumed to be trusted.
Every published result may be independently reproduced,
verified,
or challenged by additional participants.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Network Architecture}

Figure~\ref{fig:architecture}
illustrates the logical organization of the framework.

Explorer Nodes submit computational experiments
to the decentralized verification network.
The network distributes workloads among
Entropy Miners,
which execute assigned tasks independently.

To reduce the possibility of result withholding,
implementation bias,
or computational faults,
selected workloads are intentionally replicated
across multiple independent miners.
Returned observations are compared,
aggregated,
and published together with sufficient metadata
to enable subsequent independent reproduction.

This architecture separates
experiment definition,
experiment execution,
and evidence publication,
allowing individual participants
to verify every stage of the computational workflow.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[t]

\centering

\begin{tikzpicture}[
    node distance=1.4cm and 2.8cm,
    box/.style={
        draw,
        rounded corners,
        minimum width=3.5cm,
        minimum height=0.8cm,
        align=center
    },
    core/.style={
        draw,
        circle,
        minimum size=1.5cm,
        align=center
    },
    >=Stealth
]

% Explorer nodes
\node[box] (e1) {Explorer Node};
\node[box, below=of e1] (e2) {Explorer Node};

% Network
\node[core, right=3.5cm of e1.south east, yshift=-0.7cm] (net)
{Decentralized\\Network};

% Miners
\node[box, right=3.5cm of net] (m1) {Entropy Miner};
\node[box, below=of m1] (m2) {Entropy Miner};

% Connections
\draw[->] (e1.east) -- (net.west);
\draw[->] (e2.east) -- (net.west);

\draw[->] (net.east) -- (m1.west);
\draw[->] (net.east) -- (m2.west);

\draw[->] (m1.west) to[bend left=18] node[above,font=\small]{results} (net.east);
\draw[->] (m2.west) to[bend right=18] (net.east);

% Labels
\node[below=0.55cm of net,font=\small,align=center]
{
Task distribution\\
and replicated execution
};

\end{tikzpicture}

\caption{
Logical architecture of the Doomsday Explorer framework.
Explorer Nodes define computational experiments.
The decentralized verification network distributes workloads,
selectively replicates tasks,
aggregates returned observations,
and publishes reproducible evidence.
Independent replication mitigates result withholding
and enables verification of published computational results.
}

\label{fig:architecture}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Replicated Experimental Execution}

Traditional distributed computation often assumes
that each computational task requires only a single execution.
In contrast,
the Doomsday Explorer framework intentionally introduces
controlled redundancy.

A configurable fraction of submitted workloads
is executed independently by multiple miners.
Returned observations are compared
before publication,
allowing inconsistent executions,
implementation-specific behavior,
or malicious result withholding
to be detected.

The replication policy serves several purposes.

\begin{enumerate}

\item
Independent verification of published results.

\item
Detection of computational inconsistencies.

\item
Resistance to selective disclosure.

\item
Long-term measurement of experimental reproducibility.

\end{enumerate}

Importantly,
replication is treated as a scientific mechanism
rather than a consensus protocol.
Agreement between replicated executions
does not establish correctness of an underlying hypothesis;
instead,
it establishes reproducibility of the computational experiment itself.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Iterative Approximation Framework}

Entropy validation is formulated as
an iterative approximation process
rather than a binary certification decision.

Let

\[
H
=
\{H_1,H_2,\ldots,H_n\}
\]

denote competing hypotheses
regarding the behavior of an entropy source.

These hypotheses may include

\begin{itemize}

\item
existing statistical models,

\item
physical models,

\item
implementation-specific explanations,

\item
newly proposed deterministic mechanisms.

\end{itemize}

Explorer Nodes construct experiments
capable of discriminating between one or more hypotheses.

Entropy Miners execute those experiments.

Replicated execution establishes
that reported observations
are computationally reproducible.

Published evidence then updates confidence
associated with competing models.

Unlike conventional certification,
the framework never declares
a hypothesis permanently verified or falsified.
Instead,
confidence evolves continuously
as additional experiments become available.

This methodology naturally accommodates

\begin{itemize}

\item
new entropy generators,

\item
new statistical techniques,

\item
alternative physical models,

\item
independent experimental reproduction.

\end{itemize}

Consequently,
entropy assessment becomes
a continuously evolving scientific process
rather than a single certification event.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Entropy-Escape Methodology}

The proposed protocol treats entropy verification as an optimization
problem rather than a binary certification procedure.
Instead of attempting to prove that a private entropy source is
``sufficiently random,''
the framework continuously constructs increasingly accurate public approximations of currently computable high-entropy regions.
Private entropy is subsequently protected by maximizing its
computational distance from those publicly reconstructed examples.

Let

\[
\mathcal{E}
=
\{e_1,e_2,\ldots,e_n\}
\]

denote the publicly verifiable set of reconstructed entropy examples
generated by independent entropy miners.
For a private entropy value $x$,
the protocol defines the escape metric

\[
D(x,\mathcal{E})
=
\min_{e_i\in\mathcal{E}}
d(x,e_i),
\]

where $d(\cdot,\cdot)$ represents an application-dependent similarity
metric.
Security is therefore formulated as the optimization problem

\[
\max_x D(x,\mathcal{E}),
\]

subject to computational and implementation constraints.

Unlike traditional entropy certification,
the protocol does not assume that published examples are harmful.
Instead,
they serve as experimentally verified approximations of regions
containing maximal utility entropy under currently available models.
Private entropy remains secure by computationally escaping these
high-information clusters.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Known Computational Landscape and Secure Randomness}

The proposed framework evaluates entropy relative to the computational
knowledge available to a specified communicating system rather than by
assuming that randomness can be established through statistical tests
alone.

Let

\[
K_t
=
\{k_1,k_2,\ldots,k_n\}
\]

denote the \emph{known computational landscape} at time \(t\).
The set contains publicly available entropy reconstructions,
deterministic generators,
verified computational results,
intermediate artifacts,
published algorithms,
and other information available to a specified computational domain.

The computational domain may represent a decentralized verification
network,
an organization,
or any collection of communicating computational entities capable of
sharing experimental results according to an assumed communication
model.

As additional computational discoveries are independently reproduced
and published,
the landscape evolves monotonically,

\[
K_0
\subseteq
K_1
\subseteq
K_2
\subseteq
\cdots.
\]

Within the Doomsday Explorer framework,
every independently verified entropy reconstruction contributes to the
known computational landscape,
providing an increasingly accurate approximation of currently
computable high-entropy regions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Definition (Secure Randomness).}

A value \(x\) is considered \emph{secure} with respect to the known
computational landscape \(K_t\) if

\[
x
\notin
K_t,
\]

and no computationally feasible procedure available to the specified
computational domain can reconstruct \(x\) from information contained
in \(K_t\) with probability exceeding an application-defined
threshold.

Equivalently,
security may be expressed through the escape metric

\[
D(x,K_t)
=
\min_{k\in K_t}
d(x,k),
\]

where \(d(\cdot,\cdot)\) denotes an application-dependent similarity
or reconstruction metric.

A value remains secure whenever

\[
D(x,K_t)
\ge
\delta,
\]

for an application-defined security threshold \(\delta\).

Consequently,
secure randomness is formulated as a dynamic property relative to the
current computational knowledge of the specified domain rather than as
a static property of an isolated sequence.
As the known computational landscape expands,
previously secure values may cease to satisfy the required security
margin,
motivating regeneration using newly generated entropy outside the
currently reconstructed landscape.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Early-Warning Mechanism.}

Entropy miners continuously improve deterministic reconstructions of
physical entropy sources and publish representative examples together
with reproducible computational evidence.
Wallet software (or offline user verification) compares a private
secret against these published examples locally without disclosing the
secret itself.
Whenever the measured escape distance falls below an application-defined
security threshold,
the user migrates funds to newly generated entropy.
Consequently,
improvements in entropy reconstruction become defensive signals rather
than offensive capabilities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Compute-Reward Mechanism.}

Let

\[
R_i
=
f(D_i,C_i,V_i)
\]

denote the reward assigned to entropy miner $i$,
where $D_i$ measures reconstruction accuracy,
$C_i$ denotes independently replicated computational work,
and $V_i$ represents successful public verification.

Rewards increase with experimentally useful reconstructions rather than
raw computational throughput.
Workers capable of producing more accurate deterministic models receive
greater compensation,
creating an economic incentive to disclose improved entropy
reconstructions publicly instead of exploiting them privately.
The protocol therefore aligns scientific publication,
independent verification,
and participant incentives without requiring trusted intermediaries or
application-specific contractual mechanisms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Scientific Interpretation.}

Conceptually, the entropy-escape methodology adopts an approach analogous to computational
proof-of-work\cite{bitcoin2008}.
Proof-of-work expends computational effort to establish consensus and
Sybil resistance,
whereas entropy escape expends computational effort to maximize
separation from publicly reconstructed high-entropy regions in an effort to maximize separation from the known computational landscape.
Both mechanisms derive security from measurable computational work
rather than secrecy of the underlying algorithms.

Because reconstructed entropy examples remain publicly reproducible,
the methodology preserves long-term scientific value independent of any
particular application domain.
Improved physical models,
whether deterministic or stochastic,
naturally refine the public entropy landscape,
while private entropy continuously adapts by maximizing computational
distance from these experimentally verified approximations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Replica-Driven Iterative Approximation}

The proposed framework relies upon multiple independent replicas of
each computational experiment rather than a single authoritative
execution.
Replica diversity serves two purposes.
First,
independent implementations reduce the likelihood that published
results arise from implementation errors,
undocumented assumptions,
or computational faults.
Second,
multiple deterministic models provide competing approximations of the
same physical entropy source,
allowing experimental evidence to converge through iterative refinement.

Let

\[
M_1,M_2,\ldots,M_n
\]

denote independent deterministic models constructed by participating
entropy miners.
Each model produces reconstructed observations

\[
O_i=M_i(P),
\]

for a common experimental protocol \(P\).
The verification network aggregates the resulting evidence according to

\[
\mathcal{A}(P)
=
\operatorname{Aggregate}
\left(
O_1,O_2,\ldots,O_n
\right),
\]

while preserving every intermediate computation required for
independent reproduction.

Unlike majority voting,
aggregation does not imply that the most frequently reproduced model is
necessarily correct.
Instead,
replicated execution establishes reproducible evidence from which
alternative physical explanations may be evaluated.
As improved deterministic models become available,
previous reconstructions remain permanently verifiable,
allowing the approximation process to converge incrementally rather
than replacing earlier scientific results.

Consequently,
the verification framework treats scientific progress as a sequence of
publicly reproducible approximations instead of isolated experimental
claims.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Safe Proof Demonstration Paradox}

Certain classes of computational discoveries admit complete private
verification while simultaneously resisting safe public demonstration.
The difficulty does not arise from limitations of computation,
but from the relationship between reproducibility and disclosure.

Suppose a computational procedure \(S\) demonstrates the existence of
previously unrecognized vulnerabilities within a deployed entropy
generation mechanism.
Public verification of \(S\) requires sufficient information for
independent reproduction.
However,
providing a complete implementation may itself enable immediate
offensive use of the demonstrated capability,
whereas withholding essential implementation details prevents
independent verification.

The protocol therefore identifies a class of
\emph{safely unverifiable public demonstrations},
for which no practical disclosure simultaneously satisfies

\begin{enumerate}

\item independent reproducibility,

\item public verifiability,

\item and preservation of public safety.

\end{enumerate}

This paradox is independent of any specific implementation.
A demonstration lacking sufficient algorithmic detail cannot be
distinguished from an unverifiable anecdotal claim,
while a fully reproducible demonstration may substantially increase
operational risk.
Consequently,
responsible disclosure becomes fundamentally constrained by the absence
of a disclosure protocol satisfying all three properties
simultaneously.

The proposed framework addresses this limitation through iterative,
distributed private verification.
Independent participants reproduce computational results locally,
without requiring publication of operational implementations.
Consensus therefore emerges through repeated private reproductions
performed by mutually independent participants rather than through a
single publicly executable proof-of-concept.

Within the verification network,
participants express confidence not only through replicated
computational work,
but also by voluntarily allocating computational resources and
economic incentives toward defensive mitigation.
Although such consensus cannot establish scientific truth by itself,
it provides a practical mechanism for coordinating defensive action
among independently verifying participants while avoiding unnecessary
public dissemination of operational attack capabilities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Artificial Intelligence and the Replication Paradox}

Recent advances in large language models substantially reduce the
practical cost of constructing deterministic computational models.
Although current systems rarely produce complete implementations from
a single prompt, iterative interaction allows increasingly accurate
reconstructions through successive refinement, hypothesis testing, and
algorithmic correction.

Consequently, the computational difficulty of reproducing complex
entropy-generation mechanisms shifts from algorithm design toward
computational verification.
Artificial intelligence therefore acts as an accelerator for both
defensive research and offensive capability, reducing the expertise
required to construct deterministic replicas of deployed systems.

Within the proposed framework, this observation is independent of any
particular entropy source.
Whenever a physical system admits an efficient deterministic
approximation, iterative AI-assisted refinement may progressively
reduce the search space required for practical reconstruction.
The resulting methodology applies equally to embedded security
devices, industrial control systems, scientific instrumentation, and
other computationally observable processes.

This development creates a practical replication paradox.
The same computational techniques capable of improving defensive
verification also reduce the cost of constructing offensive tools.
Consequently, responsible disclosure becomes increasingly difficult as
AI systems improve their ability to synthesize executable
implementations from high-level scientific descriptions.

Rather than treating artificial intelligence as an external threat,
the proposed framework incorporates AI directly into the scientific
workflow.
Language models may assist entropy miners in constructing improved
deterministic replicas, exploring alternative physical models, and
identifying previously overlooked implementation assumptions.
Independent replication and public evidence remain the primary
verification mechanisms, while AI functions as an accelerator of the
iterative approximation process rather than as an authoritative source
of scientific truth.

The same educational mechanisms naturally extend to participant
training.
Gamified computational challenges encourage researchers, engineers,
and security practitioners to transform offensive capabilities into
publicly verifiable defensive contributions.
By rewarding improved deterministic models through open scientific
evaluation rather than undisclosed exploitation, the framework seeks
to align AI-assisted research with responsible disclosure and public
security.

From a societal perspective, the emergence of increasingly capable AI
systems suggests that large-scale automated analysis of critical
infrastructure, cryptographic implementations, and public security
systems will become progressively more practical.
The resulting ``AI races'' motivate proactive development of
reproducible defensive verification frameworks capable of evaluating
competing computational models before equivalent offensive
capabilities become commonplace.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{AI-Assisted Gamification.}

The proposed framework extends beyond automated experimentation by
introducing an AI-assisted gamification layer.
The \emph{Fun \& Profit} platform transforms entropy research,
distributed verification,
and deterministic model construction into interactive computational
challenges executed directly through conversational AI assistants.

Unlike conventional educational games,
participants contribute computationally meaningful work.
Gameplay naturally introduces concepts including entropy modelling,
iterative approximation,
distributed replication,
and reproducible scientific evidence while simultaneously encouraging
deployment of independent verification nodes within the Explorer
Network.

Artificial intelligence therefore serves both as an educational
interface and as a scientific assistant.
Players iteratively improve deterministic models,
evaluate competing hypotheses,
and construct increasingly accurate entropy replicas through guided
interaction rather than requiring prior expertise in cryptography,
signal processing,
or distributed systems.

This combination of gamification,
AI-assisted reasoning,
and reproducible scientific computation creates positive incentives for
participants to transform potentially offensive computational
capabilities into publicly verifiable defensive research.
Consequently,
community growth directly strengthens the verification network while
simultaneously improving public understanding of entropy modelling and
computational reproducibility.

The platform continuously evolves together with its AI assistants.
Interactive scenarios may construct augmented representations of
real-world environments, allowing participants to model physical,
technical, economic, and regulatory contexts within which entropy
replicas and verification protocols operate.
Consequently, educational gameplay becomes a practical mechanism for
developing reproducible scientific models rather than merely
illustrating completed research.

Economic incentives form an integral part of the learning process.
Financial decision-making, including incentive alignment and
risk--reward trade-offs inspired by option-pricing methodologies,
is incorporated directly into gameplay to demonstrate how rational
economic mechanisms can encourage disclosure, replication, and
defensive collaboration.
These educational components build upon previous work on regulatory
frameworks and financial modelling~\cite{Kondratiuk2021}.

By combining conversational AI, reproducible experimentation,
economic reasoning, and interactive world modelling, the platform
encourages participants to transform offensive computational
capabilities into publicly verifiable scientific contributions.
The resulting community simultaneously strengthens the Explorer
Network, improves deterministic entropy models, and promotes
responsible disclosure through collaborative learning rather than
adversarial competition~\cite{funAndProfit2026}.

The current implementation of the engine is publicly available through the
\emph{Fun \& Profit} platform~\cite{funAndProfit2026}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Threat Model}

The framework considers
both accidental
and adversarial sources of error.

Potential threats include

\begin{enumerate}

\item
faulty computational implementations,

\item
selective publication of favorable results,

\item
malicious participants returning fabricated computations,

\item
implementation bias,

\item
incomplete physical models,

\item
statistical overfitting.

\end{enumerate}

The framework does not assume
that replicated execution alone
proves the correctness of a scientific hypothesis.
Rather,
replication provides evidence that
published computational observations
can be reproduced independently.

Scientific conclusions remain subject
to continued experimental evaluation
as additional data become available.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experimental Methodology}

Rather than treating entropy sources as fundamentally stochastic,
the proposed framework formulates experimental verification
as an iterative deterministic reconstruction problem.
Each investigated entropy source is first represented by an idealized
physical model, after which computational search is performed over
successive deviations from that model.
The objective is not to assume randomness,
but to determine whether observed statistical behaviour can be reproduced
by increasingly accurate deterministic descriptions.

The verification protocol itself remains model-agnostic.
Any computational model capable of generating synthetic observations
may be evaluated using the same distributed execution,
replication,
and publication pipeline.
Consequently,
stochastic,
deterministic,
or hybrid physical models can be compared under identical experimental
conditions,
with all intermediate computations preserved for independent verification.

The iterative approximation process consists of four stages:

\begin{enumerate}

\item construction of an idealized physical model of the entropy source;

\item deterministic generation of synthetic observations;

\item greedy search over deviations between the generated and observed
signals;

\item publication of both reconstructed models and experimental evidence
for independent replication.

\end{enumerate}

Unlike statistical validation procedures that primarily evaluate output
distributions,
the proposed methodology evaluates the explanatory power of competing
physical models.
Statistical properties therefore emerge as consequences of reconstructed
physical processes rather than as primary assumptions regarding the
underlying entropy source.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Classical Thermal Entropy Sources}

For classical thermal generators,
the initial approximation is constructed from deterministic physical
representations of the measured signal.
In current implementations,
broadband thermal noise is represented as superpositions of elementary
basis functions,
including sinusoidal components,
after which greedy optimization searches for progressively smaller
deviations from the measured waveform.

The objective is not to reproduce every sample exactly,
but to minimize unexplained structure through successive deterministic
refinement.
Residual discrepancies become explicit experimental objects,
allowing alternative physical models to be proposed,
evaluated,
and compared using identical computational procedures.
The corresponding implementation is documented by the Doomsday Explorer
thermal entropy investigations~\cite{doomsdayThermal2026}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Quantum Experimental Models}

The same computational methodology extends to quantum experiments.
Rather than assuming intrinsic stochasticity,
the framework investigates deterministic signal models capable of
reproducing experimentally observed statistical behaviour.
Candidate representations include deterministic pulse-width modulation,
wavelet reconstruction,
and other physically motivated basis decompositions,
followed by exhaustive or greedy search over model parameters.

Within the Doomsday Explorer quantum investigation,
deterministic coincidence-detection models reproduce the CHSH statistics
observed in representative Bell-type experiments.
These computational reconstructions motivate the hypothesis that
measurement-pipeline mechanisms,
including coincidence detection,
constitute viable deterministic explanations deserving systematic
experimental evaluation alongside conventional probabilistic
interpretations~\cite{doomsdayQuantum2026,doomsdayBell2026}.

The proposed verification framework does not require adoption of any
particular physical interpretation.
Instead,
it provides a reproducible computational protocol through which
competing deterministic and stochastic models may be evaluated using
identical experimental procedures and publicly verifiable evidence.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Deterministic Reproduction of CHSH Statistics}

The quantum case study~\cite{doomsdayBell2026, doomsdayQuantum2026} demonstrates that experimentally reported
CHSH statistics can be reproduced by a fully deterministic
computational model without introducing communication between
spatially separated particles.
The objective is not to postulate a new interpretation of quantum
mechanics, but to demonstrate that deterministic computational
reconstructions constitute experimentally testable competing models.

Instead of representing the quantum state through a complex-valued
wave function, the implemented model constructs deterministic
pulse-width modulated signal representations whose relative delay
corresponds to the angular difference between measurement settings.
Since Bell-type correlations depend only upon relative detector
orientation, the computational model is formulated directly in terms
of detector-angle differences rather than absolute orientations.
Probabilities are represented as deterministic densities encoded by
pulse-width modulation, producing reproducible signal trajectories
throughout the simulation.

Synthetic detector outputs are subsequently processed by a deterministic
coincidence-detection procedure.
Within this implementation, the coincidence-selection logic alone is
sufficient to reproduce the characteristic CHSH correlations reported
for representative Bell-type experiments, while no communication
channel between the simulated particles is introduced.
Consequently, the computational model provides a constructive
deterministic reproduction of the target statistics using only local
signal generation together with deterministic event-selection logic.
The implementation is described in the accompanying quantum notebook
and Scala reference implementation.

Within the proposed verification framework, this result should be
viewed as a reproducible computational hypothesis rather than a
terminal conclusion.
If deterministic coincidence-detection models reproduce the observed
statistics, subsequent experimental investigation reduces to
determining whether equivalent event-selection mechanisms are present
within physical measurement pipelines.
The framework therefore enables competing physical explanations to be
evaluated through identical computational procedures, independent
replication, and publicly reproducible evidence.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evidence Accumulation}

Unlike conventional certification,
which typically culminates in a pass/fail decision,
the proposed framework accumulates evidence continuously.

Each completed experiment contributes

\begin{itemize}

\item reproducible computational observations,

\item associated experimental parameters,

\item replication statistics,

\item independent verification records.

\end{itemize}

Together,
these observations form an evolving public corpus
through which competing entropy models may be evaluated.

The framework therefore separates

\begin{enumerate}

\item experimental observation,

\item statistical interpretation,

\item scientific conclusion.

\end{enumerate}

This separation permits multiple researchers
to interpret identical experimental data
using different theoretical models
without requiring modification of the underlying infrastructure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Relationship to Existing Standards}

The proposed framework is intended to complement,
rather than replace,
existing certification methodologies.

Statistical testing frameworks,
including NIST SP~800\cite{nist80022} series recommendations,
remain valuable engineering tools for detecting
many classes of implementation defects,
bias,
and statistical anomalies.

Similarly,
physical characterization remains essential
for understanding entropy-generating devices.

The Doomsday Explorer framework addresses a different question.

Rather than asking whether a generator satisfies
a predefined statistical standard,
the framework asks whether competing scientific explanations
continue to remain consistent
with an expanding body of independently reproducible evidence.

This distinction transforms entropy validation
from a finite certification procedure
into a continuously evolving experimental process.

The framework is designed to remain useful regardless of whether existing entropy models are ultimately confirmed, refined, or replaced, since every hypothesis is evaluated through the same reproducible computational methodology.

\section{Discussion}

Entropy research occupies an unusual position
at the intersection of mathematics,
physics,
statistics,
and engineering.

No finite experimental program
can conclusively establish
the unpredictability of a physical process.
Likewise,
no individual statistical anomaly
necessarily invalidates an existing physical model.

Consequently,
scientific progress requires
continuous experimentation,
independent replication,
and transparent publication of evidence.

The Doomsday Explorer framework
is motivated by this philosophy.

Its objective is not to replace established standards,
nor to promote any specific interpretation
of classical or quantum physics.
Instead,
it provides computational infrastructure
through which competing hypotheses
may be evaluated using identical,
publicly reproducible experimental procedures.

The framework therefore shifts emphasis
from authority-based validation
toward evidence-based refinement,
allowing confidence in entropy models
to evolve as additional computational
and experimental observations become available.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Applications and Representative Investigations}

The Doomsday Explorer project applies the proposed verification
framework to a growing collection of entropy-related investigations.
Rather than publishing isolated experimental results,
each investigation is expressed as a reproducible computational
workflow that can be independently replicated,
extended,
and re-evaluated as new theoretical models and experimental evidence
become available.

Representative application domains currently include

\begin{itemize}

\item
classical thermal-noise entropy generators,

\item
hardware true random number generators,

\item
operating-system entropy sources,

\item
quantum random number generators,

\item
Bell-type experimental protocols,

\item
entropy estimation methodologies,

\item
statistical certification procedures.

\end{itemize}

Explorer Nodes formulate reproducible computational experiments,
while independent participants execute assigned workloads.
Selected tasks are intentionally replicated,
and returned observations are published together with sufficient
experimental metadata to permit independent verification and future
reproduction.

Experimental specifications,
analysis software,
input datasets,
and computational observations are intended to remain publicly
reproducible wherever appropriate,
allowing competing scientific interpretations to be evaluated using
the same underlying body of evidence.

Consequently,
scientific conclusions evolve through continued experimentation and
independent replication rather than through isolated publications or
one-time certification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Limitations}

The proposed framework intentionally separates
scientific methodology
from scientific conclusion.

Replicated computation does not,
by itself,
establish the correctness of any physical theory,
statistical model,
or entropy source.
Instead,
it establishes that published computational observations
may be independently reproduced under identical experimental
conditions.

Likewise,
statistical inconsistency does not necessarily imply
deterministic behavior,
nor does statistical consistency establish true unpredictability.

Scientific interpretation therefore remains dependent upon
theoretical analysis,
experimental design,
and continued independent investigation.

The framework should consequently be viewed
as infrastructure for entropy research
rather than as a replacement for
existing cryptographic standards
or physical validation procedures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Future Work}


The present work establishes a decentralized computational framework
for iterative verification of entropy-related hypotheses.
Its primary contribution is methodological,
providing common infrastructure through which competing computational
models may be evaluated using reproducible experimentation and
independent replication.

Several directions naturally emerge from this foundation.

First,
the framework may be extended to additional entropy sources,
including emerging hardware entropy devices,
hybrid physical systems,
large-scale distributed infrastructures,
and future quantum technologies.
Improved experimental protocols,
replication strategies,
and verification mechanisms may further increase both computational
efficiency and scientific reproducibility.

Second,
the deterministic reconstruction methodology introduced by the
framework motivates specialized investigations into the physical nature
of entropy,
randomness,
and scientific observation.
Future publications may evaluate competing physical models,
measurement procedures,
and experimental methodologies using the common computational
infrastructure presented here,
while remaining agnostic with respect to any particular physical
interpretation.

Third,
the security implications of continuously evolving computational
knowledge warrant dedicated investigation.
Future work may formalize the relationship between known computational
landscapes,
entropy reconstruction,
adaptive key generation,
and long-term cryptographic security under progressively improving
computational capabilities.

Fourth,
the framework motivates further research in human--computer
interaction,
particularly with respect to AI-assisted scientific exploration.
The \emph{Fun \& Profit} platform demonstrates how conversational AI,
interactive simulation,
and gamified experimentation may enable participants to contribute
meaningful scientific computation while simultaneously improving their
understanding of distributed verification,
entropy modelling,
and reproducible research.
Future work will investigate collaborative workflows involving both
human participants and AI agents operating as scientific assistants
within decentralized verification networks.

Finally, the interdisciplinary nature of the project naturally
motivates growth into specialized research programs spanning
distributed systems, cryptography, experimental physics,
artificial intelligence, and human--computer interaction.
The present work establishes a common computational foundation upon
which these investigations may evolve independently while sharing a
reproducible verification infrastructure.

As the underlying methodologies mature and individual components become
sufficiently separated from security-sensitive investigations, future
publications may increasingly focus on domain-specific theoretical,
experimental, and engineering contributions. Such work naturally lends
itself to broader collaboration among researchers with complementary
expertise, while the underlying verification framework continues to
provide a common basis for reproducible scientific evaluation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

Entropy remains one of the most fundamental assumptions
underlying modern cryptographic security.
Although existing certification methodologies provide
substantial confidence in deployed entropy sources,
their conclusions necessarily depend upon
experimental assumptions,
physical models,
and observable statistical behavior.

This paper has presented
Doomsday Explorer,
a decentralized framework for
iterative verification of entropy-related hypotheses.

Rather than introducing another statistical randomness test,
the framework establishes
an open scientific infrastructure
through which competing models
may be evaluated using identical,
publicly reproducible computational procedures.

Explorer Nodes formulate reproducible experiments,
Entropy Miners execute computational workloads,
and selective replication enables
independent verification of published observations.
Confidence in competing hypotheses
therefore evolves through
continuous evidence accumulation
rather than centralized authority
or one-time certification.

The framework is intentionally agnostic
with respect to individual physical models.
Classical entropy sources,
quantum entropy sources,
and future experimental systems
are all treated as subjects
of continuous scientific investigation.

By combining decentralized computation, independent replication, reproducible scientific methodology,
and transparent publication,
the proposed methodology
extends entropy research
from isolated experimental studies
toward an evolving,
community-driven process
of scientific verification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Data Availability}

The Doomsday Explorer project publishes
experimental software,
datasets,
documentation,
and computational results
through publicly accessible repositories
to enable independent reproduction
of the experiments described in this work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Project Identity}

The Doomsday Explorer project\cite{doomsdayThermal2026} is identified by the following
Bitcoin Taproot address:

\begin{center}
\texttt{bc1qekvmkczge3hxrvwdf2lj3yyvgjnparn3fdf9lg}

\texttt{Message: "Doomsday Explorer Project for Bitcoin: https://github.com/dk14/crypto/tree/main/chats/btc-audit"}

\texttt{Signature: IHdq/tIQtQeimfF92NOyOOdz2/iq2YR6qjD8vLgHWK3GGGETKX76L0e4Tvgtb1fOHrbLiW87QYIuOdCKYbSvmpA=}
\end{center}

This address provides a persistent cryptographic identifier for
the project. Public software releases, experimental reports,
and related announcements may be authenticated using signatures
generated by the corresponding private key.

\section*{Acknowledgements}

The authors thank
members of the open scientific and cryptographic communities
whose independent analysis,
discussion,
and replication efforts
continue to improve
the quality,
reproducibility,
and transparency
of entropy research.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plain}
\bibliography{references}

\end{document}